mathml: Translate R expressions to MathML and LaTeX/MathJax

### 2022-12-12 Draft3.Rmd
clean up

```{r add, echo=FALSE}
op <- list(left=quote(add_left(a + b)), right=quote(add_right(a + b)), list=quote(add(c)))
m <- lapply(op, FUN=mathjax, flags=list(cat=FALSE))

>>>>

```{r add, echo=FALSE}
op <- list(left=quote(add_left(a + b)), right=quote(add_right(a + b)))
m <- lapply(op, FUN=mathjax, flags=list(cat=FALSE))
